\documentclass[]{scrartcl}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage[ddmmyyyy]{datetime}
\renewcommand{\dateseparator}{.}

\newcommand{\R}{\mathbb{R}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\bw}{\mathbf{w}}
\newtheorem{prop}{Proposition}
\setlist[enumerate,1]{label=\bfseries\arabic*)}

\author{Prof. Marius Kloft \and TA:Billy Joe Franks}
\title{Machine Learning I: Foundations \\ Exercise Sheet 2}
\date{\today\\Deadline: 12.05.2020}
\begin{document}
\maketitle

\begin{enumerate}

\item \textbf{(MANDATORY) 10 Points}\\
	In this exercise we will consider the soft-margin SVM
	\begin{alignat}{2}
   \min~&  \frac{1}{2}\left\lVert\bw\right\rVert^2+C\sum_{i=1}^n \xi_i\nonumber \\
   \text{s.t.}~  & 1-\xi_i-y_i(\bw^T\bx_i+b) \leq 0,~-\xi_i\leq 0,~\forall i\in\{1,\dots,n\}\nonumber
\end{alignat}
Let $a\in(2,-1)$, consider the one-dimensional datapoints $(2,1), (a,1), (-2,-1)$. For each datapoint the second value is the label. This is a binary classification dataset. We will investigate the behavior of $C$.
\begin{enumerate}
\item Determine for $(1)~w=\frac{1}{2}, b=0$ and $(2)~w=\frac{2}{a+2}, b=\frac{2-a}{a+2}$ the objective function depending on $a$ and $C$.
\item For which value of $C$ is $(1)$ uniformly better than $(2)$, i.e. $\forall a\in (2,-1)$. For which value of $C$ is $(2)$ uniformly better than $(1)$?
\textbf{Hint:} Explicitly evaluating the intersections of functions is quite involved in this case. Consider using a plotting tool to compare the functions. Prove or argue whatever you find post hoc.
\item Conclude how $C$ influences the optimization problem. Justify your conclusion using at most 5 sentences.
\end{enumerate}

\item Let $f(a_1,a_2, \cdots, a_n) = \ln{( e^{a_1}+ e^{a_2}+\cdots+ e^{a_n})}$. Show that $f$ is convex.

\item Using any techniques you have learned from class, determine the domain on which the function $f(x,y) = xy^3$ is convex, i.e. for which combination of $x$ and $y$ is $f(x,y)$ convex?

\item Solve programming task 2.
\end{enumerate}
\end{document}